Contextual Combinatorial Cascading Bandits

### 2016-01-13 contextual combinatorial cascading bandits.tex
update experiment structure
update experiment -network

% my settings
\usepackage{amssymb,amsfonts,amsmath,bbm}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\usepackage{ifthen}
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames]{xcolor}

@@

>>>>

% my settings
\usepackage{amssymb,amsfonts,amsmath,bbm}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\usepackage{ifthen}
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{epstopdf}
%\usepackage{epsfig}
%\usepackage{times}
%\usepackage{helvet}
%\usepackage{courier}
%\usepackage{graphicx,subfigure}
%\usepackage{pdfpages}
%\usepackage{multirow}
%\usepackage{multicol}

@@

We evaluate $C^3$-UCB in three experiments.

\subsection{Synthetic}

\subsection{MovieLens}

\subsection{Network Routing}

In the last experiment, we evaluate $C^3$-UCB on a problem of network routing. We experiment on six networks from the {\it RocketFuel} dataset\cite{spring2004measuring}.

The ground set $E$ is the set of links in the network and the feasible action set $\cS$ is the set of all paths in the network. Before learning, the environment randomly chooses a $d$-dimensional vector $\theta \in [0,1]^d$. At each time $t$, any link $e$ is assigned with a random $d$-dimensional context vector $x_{t,e}$ and the corresponding latency follows exponential distribution with mean $1-\theta^{\top}x$, which has been scaled into $[0,1]$. We call the latency is {\it high} if it is larger than a threshold $\tau$. A pair of source and terminal nodes $(v_s, v_t)$ are chosen randomly. The agent recommends a feasible path $A = (a_1,...,a_{|A|})$ from $v_s$ to $v_t$ with expected reward
$$
\prod_{k=1}^{|A|} (1- \exp(-\frac{\tau}{1-\theta^{\top}x_{t,a_k}})).
$$
Notice that the expression is not of the form $\prod_{k=1}^{|A|}\theta_*^{\top}x_{t,a_k}$ in our model. However, our algorithm could also apply to it.

\begin{figure}
	\centering
	\subfigure[Network 1755]{
		\includegraphics[height = 1.8cm, width = 2.6 cm]{network3-1.eps}}
	\subfigure[Network ]{
		\includegraphics[height = 1.8cm, width = 2.6 cm]{network4-1.eps}}
	\subfigure[Network]{
		\includegraphics[height = 1.8cm, width = 2.6 cm]{network4-1.eps}}
	\caption{sample number and accuracy}
	\label{fig:sample number} % 用于交叉引用
\end{figure}
